\begin{entry}{Initial Script}{March 1, 2021}
    \objective
    Get GridAPPS-D running from a script.

    \outline

    Today's tasks were:
        \begin{itemize}
            \item Figure out how to set the configuration of a model from the python script
            \item Connect to and run the script

        \end{itemize}

    \procedures

        First, I needed the command to get all the feeders in the database:
        \begin{minted}{sql}
            # list all the feeders, with substations and regions - DistFeeder
                PREFIX r:  <http://www.w3.org/1999/02/22-rdf-syntax-ns#>
                PREFIX c:  <http://iec.ch/TC57/CIM100#>
                SELECT ?feeder ?fid ?station ?sid ?subregion ?sgrid ?region ?rgnid WHERE {
                 ?s r:type c:Feeder.
                 ?s c:IdentifiedObject.name ?feeder.
                 ?s c:IdentifiedObject.mRID ?fid.
                 ?s c:Feeder.NormalEnergizingSubstation ?sub.
                 ?sub c:IdentifiedObject.name ?station.
                 ?sub c:IdentifiedObject.mRID ?sid.
                 ?sub c:Substation.Region ?sgr.
                 ?sgr c:IdentifiedObject.name ?subregion.
                 ?sgr c:IdentifiedObject.mRID ?sgrid.
                 ?sgr c:SubGeographicalRegion.Region ?rgn.
                 ?rgn c:IdentifiedObject.name ?region.
                 ?rgn c:IdentifiedObject.mRID ?rgnid.
            }
            ORDER by ?station ?feeder
        \end{minted}

        Then I wrote the code in the LogTest.py file to set up the simulation:
        \begin{minted}{python}
            run_config_13 = {
                "power_system_config": {
                    "GeographicalRegion_name": "_73C512BD-7249-4F50-50DA-D93849B89C43",
                    "SubGeographicalRegion_name": "_ABEB635F-729D-24BF-B8A4-E2EF268D8B9E",
                    "Line_name": "_49AD8E07-3BF9-A4E2-CB8F-C3722F837B62"
                },
                "application_config": {
                    "applications": []
                },
                "simulation_config": {
                    "start_time": "1570041113",
                    "duration": "120",
                    "simulator" : "GridLAB-D",
                    "timestep_frequency": "1000",
                    "timestep_increment": "1000",
                    "run_realtime": True,
                    "simulation_name": "ieee123",
                    "power_flow_solver_method": "NR",
                    "model_creation_config":{
                        "load_scaling_factor": "1",
                        "schedule_name": "ieeezipload",
                        "z_fraction": "0",
                        "i_fraction": "1",
                        "p_fraction": "0",
                        "randomize_zipload_fractions": False,
                        "use_houses": False
                    }

                },
        \end{minted}

        Then I wrote the code to start the simulation.

    \parameters

    See above

    \observations

        Need "{\usepackage[outputdir=auxil]{minted}}" for minted in this document, as well as to change the auxil
    folder to the one in the journal folder.


    \results

    Done. Now able to run a 13-node simulation from the script.

\end{entry}